The binary liquid model for gravity-driven microchannel simulations

### 2010-11-04 Text/paper.tex
Adding results for the bubble length. Need to add qualitative pictures from Kreutzer and Yang.

\section{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for the range of capillary
numbers. Because of limiting computational factors as memory and the
performance we cannot go to the range of small
capillary numbers. However, all the other methods were validated across the
small capilary numbers and extended for the range of capillary numbers from
$0.005$ to $10.0$. Our goal is to compare the film thickness over the capillary
range from $0.03$ to $0.8$, which is a computationally reasonable task.  For the
benchmark
results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
\begin{equation}
0.04,0.06,0.08,0.1,0.12,0.13,0.15\,.
\end{equation}
To perform numerical simulations we refer
to
grid refinement section where we obtained that the interface width should be
at most $50$ percent of the interface width. Therefore the grid was chosen as
$202 \mathrm{x} 3001$. $5$ lattice boltzmann units do not occupy more than $60$
percent of the effective width. Because the simulation get unstable with
smaller grids and larger gradients, all the capillary number simulations were
performed on the grid chosen. To properly initialize the force gradient the
proportionality law was utilized. For instance, with the forcing
$6\,10^{-6}/16$ was chosen for the grid to obtain predicted capillary number as
$0.005$. Therefore, one can obtain the initial forcing for other grids using
simple correlations: 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{bubble}\\
&U_{bubble} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\ 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{N_y^2},
\end{aligned}
\end{equation}
where the index $lit$ stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. The grid number $N_y$ is not
involved as because the simulations are conducted on the same grid.
Therefore,the pressure gradient can be obtained through the capillary numbers
ratio:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{lit}}{0.05}
\end{equation}
The film width is initialized through the capillary numbers ratio as well:
\begin{equation*}
w=12 \frac{Ca_{lit}}{0.05}
\end{equation*}
The results were obtained after $200,000$ steps. Film thicknesses were obtained as $0.042$,$0.066$, $0.085$, $0.077$, $0.123$, $0.153$, $0.164$, $0.173$ with the bubble center velocities as $0.0022$, $0.0041$, $0.0068$, $0.0055$, $0.0185$, $0.0388$, $0.0592$, $0.0782$. Based on the obtained center velocities the capillary numbers 
are formed as $0.039$,$0.072$,$0.120$,$0.098$,$0.328$,$0.686$,$1.046$,$1.383$. Those capillary numbers are overpredicted but the obtained lengths are overpredicted as well due to the improper body force imposement. 
We extracted data from \cite{giavedoni-numerical,heil-bretherton} and compared it with the simulation. The results are shown in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary/capillaries_comparison.eps}
\caption{The comparison between simulation results and results from \cite{giavedoni-numerical} and \cite{heil-bretherton}. One can see the reasonable agreement. The film thickness against the capillary number range is presented.\label{fig:capillary:comparison}}
\end{figure}

\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. We
haven't found significant differences with the results obtained earlier. The
comparison for the liquid thicknesses is presented on Fig.
\ref{fig:capillary:viscous}. Therefore one can validate the assumption that in
the low capillary flow regime the density ratio is not involved. As well the
gas-liquid viscosity ratio of the order $10$ is enough to obtain results
consistent with the Bretherton/Taylor problem. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary_Viscous/capillaries_viscous.eps}
\caption{The widths versus capillary number comparison for
$\frac{\mu_{liq}}{\mu_{gas}}=10$ and $\frac{\mu_{liq}}{\mu_{gas}}=20$. The
results show good consistency and agreement.\label{fig:capillary:viscous}}
\end{figure}

>>>>

\subsection{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for the range of capillary
numbers. Because of limiting computational factors as memory and the
performance we cannot go to the range of small
capillary numbers. However, all the other methods were validated across the
small capilary numbers and extended for the range of capillary numbers from
$0.005$ to $10.0$. Our goal is to compare the film thickness over the capillary
range from $0.03$ to $0.8$, which is a computationally reasonable task.  For the
benchmark
results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
\begin{equation}
0.04,0.06,0.08,0.1,0.12,0.13,0.15\,.
\end{equation}
To perform numerical simulations we refer
to
grid refinement section where we obtained that the interface width should be
at most $50$ percent of the interface width. Therefore the grid was chosen as
$202 \mathrm{x} 3001$. $5$ lattice boltzmann units do not occupy more than $60$
percent of the effective width. Because the simulation get unstable with
smaller grids and larger gradients, all the capillary number simulations were
performed on the grid chosen. To properly initialize the force gradient the
proportionality law was utilized. For instance, with the forcing
$6\,10^{-6}/16$ was chosen for the grid to obtain predicted capillary number as
$0.005$. Therefore, one can obtain the initial forcing for other grids using
simple correlations: 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{bubble}\\
&U_{bubble} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\ 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{N_y^2},
\end{aligned}
\end{equation}
where the index $lit$ stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. The grid number $N_y$ is not
involved as because the simulations are conducted on the same grid.
Therefore,the pressure gradient can be obtained through the capillary numbers
ratio:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{lit}}{0.05}
\end{equation}
The film width is initialized through the capillary numbers ratio as well:
\begin{equation*}
w=12 \frac{Ca_{lit}}{0.05}
\end{equation*}
The results were obtained after $200,000$ steps. Film thicknesses were obtained as $0.042$,$0.066$, $0.085$, $0.077$, $0.123$, $0.153$, $0.164$, $0.173$ with the bubble center velocities as $0.0022$, $0.0041$, $0.0068$, $0.0055$, $0.0185$, $0.0388$, $0.0592$, $0.0782$. Based on the obtained center velocities the capillary numbers 
are formed as $0.039$,$0.072$,$0.120$,$0.098$,$0.328$,$0.686$,$1.046$,$1.383$. Those capillary numbers are overpredicted but the obtained lengths are overpredicted as well due to the improper body force imposement. 
We extracted data from \cite{giavedoni-numerical,heil-bretherton} and compared it with the simulation. The results are shown in Fig. \ref{fig:capillary:comparison}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary/capillaries_comparison.eps}
\caption{The comparison between simulation results and results from \cite{giavedoni-numerical} and \cite{heil-bretherton}. One can see the reasonable agreement. The film thickness against the capillary number range is presented.\label{fig:capillary:comparison}}
\end{figure}

\subsection{The film variation over the bubble}
Though this section

\subsection{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. We
haven't found significant differences with the results obtained earlier. The
comparison for the liquid thicknesses is presented on Fig.
\ref{fig:capillary:viscous}. Therefore one can validate the assumption that in
the low capillary flow regime the density ratio is not involved. As well the
gas-liquid viscosity ratio of the order $10$ is enough to obtain results
consistent with the Bretherton/Taylor problem. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary_Viscous/capillaries_viscous.eps}
\caption{The widths versus capillary number comparison for
$\frac{\mu_{liq}}{\mu_{gas}}=10$ and $\frac{\mu_{liq}}{\mu_{gas}}=20$. The
results show good consistency and agreement.\label{fig:capillary:viscous}}
\end{figure}
